On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-16 7_results_RQ3.tex
And some more

The third research question RQ\ref{item:rq2} concerns the direct
application of magnitude estimation relevance judgments for the
evaluation of IR systems, by considering their use for calibrating
gain levels in two most widely-used gain-based IR evaluation metrics, nDCG
and ERR.

@@

Given that the agreement between our magnitude scores, TREC judgments
and Sormunen's judgments is not perfect, it is reasonable to expect
that relative system effectiveness orderings computed with each of
these as a basis may differ.
We first examine the correlation between system orderings using
magnitude estimation scores and TREC relevance as gain values, as for
both these judgment sets we have nearly complete coverage of the top 10
documents of all runs submitted to TREC-8, for our 18 judged topics.
% In the conference version of this paper~\cite{ME-SIGIR15} we showed the
% system scores (mean over all 18 topics) using median magnitude
% estimation scores per document (x-axis), and binary TREC categories
% (y-axis).
% This gave a result similar to Figure~\ref{fig:runs-rerank-median3best}.
% Unjudged documents were assumed to be irrelevant, as is common practice
% when using TREC data.
% \aht{What do you think of this almost self-referential style?}
% 
% Here we make a small alteration to the aggregation of the ME scores to
% get a single score for a document.
Rather than taking the median of all scores assigned to a document, we
take the median of scores taken from the three units that have document
orderings that have the highest agreement with the TREC orderings, or
Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement as
computed in Section~\ref{sec:internal-agreement}, with ties broken in favor
of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see should be more
attributable to the scale of the gain values, rather than perturbations in
document orderings given by different gain values.
\textcolor{red}{Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply took the median 
of all units, even if the unit wildly disagreed with the ordering of documents
given by the categorical judgments. This revised methodology accounts for the 
differences between the figures and tables in this section and 
in the previous paper.}

@@

The previous section showed that using magnitudes as gain led to
changes in the ranking of systems using different metrics, even when
only aggregating over magnitude judgments that agreed with individual pairwise
document rankings of the original categorical scale.
There is, however, substantial variation in the magnitudes assigned to documents
by our judges.
Perhaps using magnitudes from different judges would lead to different 
system rankings. 
As we have at least 10 judgments per topic-document pair, we can
re-sample individual scores many times, recompute system orderings, and
get a distribution of $\tau$ values.
The results are shown in Figure~\ref{fig:runs-rerank-resample}: the
correlations between system orderings seen in the previous section sit about in the middle 
of these distributions.
The spread of the distributions reflect the wide range of individual variation -- differences in
perceptions of relevance -- that in turn leads to a wide range of
$\tau$ values.
% \aht{I don't think I need to alter this as the median-of-best-3 aggregator falls withint he
% boxes.}

@@

\textcolor{red}{
Generally the correlations between the system rankings based on 
categorical and ME gain values are higher when the wide judgments
are used as opposed to the narrow judgments.
This contradicts our expectations from 
Table~\ref{tab:scaling-cats}, which indicated that
a larger scale of gains led to a decrease in correlations.
This confirms that a simple argument based on the scale 
of judgments is not sufficient in explaining different system orders, 
although the number of topics used here is small (12).
We examine this further in the next section.
}

>>>>

The third research question RQ\ref{item:rq2} concerns the direct
application of magnitude estimation relevance judgments for the
evaluation of IR systems, by considering their use for calibrating
gain levels in two widely-used gain-based IR evaluation metrics, nDCG
and ERR.

@@

Given that the agreement between our magnitude scores, TREC judgments
and Sormunen's judgments is not perfect, it is reasonable to expect
that relative system effectiveness orderings computed with each of
these as a basis may differ.
We first examine the correlation between system orderings using
magnitude estimation scores and TREC relevance as gain values, as for
both these judgment sets we have nearly complete coverage of the top 10
documents of all runs submitted to TREC-8, for our 18 judged topics.
% In the conference version of this paper~\cite{ME-SIGIR15} we showed the
% system scores (mean over all 18 topics) using median magnitude
% estimation scores per document (x-axis), and binary TREC categories
% (y-axis).
% This gave a result similar to Figure~\ref{fig:runs-rerank-median3best}.
% Unjudged documents were assumed to be irrelevant, as is common practice
% when using TREC data.
% \aht{What do you think of this almost self-referential style?}
% 
% Here we make a small alteration to the aggregation of the ME scores to
% get a single score for a document.

Rather than simply taking the median of all ME scores assigned to a
document, we take the median of scores taken from the three units that
have document orderings that have the highest agreement with the TREC
orderings, or Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement
as computed in Section~\ref{sec:internal-agreement}, with ties broken
in favor of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see
should be more attributable to the scale of the gain values, rather
than perturbations in document orderings given by different gain
values.
\textcolor{red}{Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply
took the median of all units, even if the unit wildly disagreed with
the ordering of documents given by the categorical judgments.
This revised methodology accounts for the differences between the
figures and tables in this section and in the previous paper.}

@@

The previous section showed that using magnitudes as gain led to
changes in the ranking of systems using different metrics, even when
only aggregating over magnitude judgments that agreed with individual pairwise
document rankings of the original categorical scale.
There is, however, substantial variation in the magnitudes assigned to documents
by our judges.
Perhaps using magnitudes from different judges would lead to different 
system rankings. 
As we have at least 10 judgments per topic-document pair, we can
re-sample individual scores many times, recompute system orderings, and
get a distribution of $\tau$ values.
The results are shown in Figure~\ref{fig:runs-rerank-resample}: the
correlations between system orderings seen in the previous section sit around the middle 
of these distributions.
The spread of the distributions reflect the wide range of individual variation -- differences in
perceptions of relevance -- that in turn leads to a wide range of
$\tau$ values.
% \aht{I don't think I need to alter this as the median-of-best-3 aggregator falls withint he
% boxes.}

@@

\textcolor{red}{ Generally the correlations between the system rankings
based on categorical and ME gain values are higher when the wide
judgments are used as opposed to the narrow judgments.
This contradicts our expectations from Table~\ref{tab:scaling-cats},
which indicated that a larger scale of gains led to a decrease in
correlations.
This confirms that a simple argument based on the scale of judgments is
not sufficient to explain the different system orderings, although the
number of topics used here is small (12).
We examine this further in the next section.
}
